---
title: "Final Manifesto"
author: "Raju Adhikari and Devvart Poddar"
date: "May 13, 2017"
output: 
  pdf_document:
    number_sections: true
    toc: true

bibliography: references.bib
nocite: "@Merz2016"
---

\pagebreak

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

# try(setwd("C:/RajuPC/Content Analysis/Final/QCA_Final_Project"))
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE,
  error = FALSE, cache = 3, fig.pos = 'h', fig.align = 'center',
  fig.width = 6, fig.height = 3)
knitr::opts_knit$set(root.dir = '/home/devvart/Desktop/QCA_Final_Project/')
  
library(manifestoR)
library(knitr)
library(fBasics)
library(dplyr)
library(ggplot2)

```

```{r wd, echo = FALSE}
mp_setapikey("manifesto_apikey.txt")

source("packages.R")
```

```{r, include = FALSE}
df1 <- mp_maindataset(version = "current", south_america = FALSE, download_format = NULL, apikey = NULL)

df2 <- df1 %>%
  dplyr::filter(countryname == "Germany") %>%
  dplyr::filter(partyname == "Social Democratic Party of Germany" | partyname == "Christian Democratic Union/Christian Social Union" | partyname == "Free Democratic Party")
```

# Introduction:

In this paper, we aim to understand the intricate relationship between the political parties and the voters based on the topics that political parties often use as a means to incentivize voters. From a more philosophical standpoint, different political parties are entities with similar goals but different means of achieving them. These means can be construed as the mandates of these parties. For example, the mandate of left-wing parties is to achieve social and economic justice through government intervention and welfare systems, while that of right-wing parties is to achieve social and economic justice through less intervention and allowing the market to function freely. While taking up these different approaches (means), the parties often reach out to the voters through a selection of ideas, topics, and verbiage that is unique to their philosophy. In this paper, we analyze these "contents" of political rhetoric of three main German national parties. We will use the Manifesto Dataset to first see the differences between the three parties in terms of different social and political agendas over the years. Second, we will see which topics do these parties use frequently in order appeal to the voters. Then, we will combine this data with the topic distribution dataset obtained from newspaper articles to analyze the role of media in facilitating the interaction between political parties and voters.

The role of media is stronger than ever before in shaping people's political ideologies, which makes them one of the most important bridge between the voters and the politicians. A media is a powerful store house of information, that both sides can use for their benefit. While it is often easy to know precisely the belief or the mandate of a political party, it is not so often to make similar inferences about voters. Voters are enigmatic, they may or may not turn out to vote driven by a plethora of factors, and there is never a hard and fast way to know who they might vote for. In that regard, we assume that media can play the role of proxy for the voters. If certain topics are often repeated in the media, then that could mean that voters are interested in those topics. Through the manifesto dataset, we aim to analyze the differences "between" the parties, while through the topic distribution dataset, we aim to analyze the differences "between" the parties and the media.   

# Data and Methodology

## Data

The data for this en devour is sourced from multiple sources. The primary dataset to analyse the differences in party ideology comes from the Comparative Manifesto Project. The project addresses the collection and the comparative content analysis of parties’ manifestos, covering over 1000 parties from 1945 onward in over 50 countries on five continents. The dataset is limited to the major political parties in Germany for our analysis. Furthermore, due to the lack of historical archives to media articles, as well as issues with storing and analysing the huge corpora of text, the data is further limited to elections post 2000 for comparison with trends in media.

Dataset for media is collected from scraping Der Spiegel, a daily left-leaning German news publisher. Der Speigel is unique in their free access to their archives as well as their pre-categorization of the news articles. All articles on Der Spiegel are categorized into topics such as politics, sports, culture ..., with the topic of politics being further categorized into domestic and international political news. The pre-processing of data into broad categories, allows us to focus on collecting only the relevant dataset towards our analysis, without the risk of bias. Thus, we scrape all article which relate to domestic politics from 2000 onward.

The dataset on news is further limited to only articles which were published 1 year before each election. Thus for the 2002 elections, articles published in between the periods September 2001 and 2002 were scraped, and so forth. This is led by the assumption of *limited memory*; voters and individuals are constrained by their limited memory when making decisions. Studies have noted the consumer choice to be bounded by small term memory and processing skills [@James1986; @Dick2017]. In a similar vein, voters are limited to recent memory when making a choice. Similarly, individuals do not focus on historical events, but on the events that occur closer to elections. Thus it would be imperative to assume that the events that are closer to elections, and the media coverage of these events, should drive the narrative of political parties as well. It is however important to note that the use of 1 year before each election is an assumption and may be violated. There are no studies which look at the limits of long-term memory when it concerns towards political choice, and the use of different data intervals are left to future research.

The website is scraped using Scrapy, a web scraping framework written in Python. The dataset for news articles post 2000 onward is encompasses nearly 70000 observations, though they are limited to nearly 14000 for our analysis. The data as well as the scraping codes are available on Github. 

## Methodology

The analysis can be broken into two steps; the first step will look at analysing the differences withing the priorities for each major party in Germany. We will use the CMP dataset to work on the differences between the parties using both a measure of right-left slant of the topic, as well as the importance of that topic for the party, measured using the distribution of the different topics. 

The next step would be to compare the individual distribution for the parties with the distributions derived from news articles. High correlations between the two would imply a convergence between the different parties on major topics, while low correlations would imply a dichotomy between the issues of the hour and the response to the parties to those issues. 

A brief divergence must be made here to defend the methods followed by the paper. We use a topic model to differentiate the different topics in news across the different years, but we do not provide them with a left or a right leaning political score. There are two reasons for this approach; Firstly there is reason to believe that the scores might be biased for our dataset. As explained earlier, Der Spiegel is a left leaning daily news publisher in Germany. As such it is not difficult to believe that the scores may be biased against right and conservative parties in Germany. 

Secondly, we believe that it is a difficult task to compare the political scores between media and political parties to explain the convergence or dichotomy between the parties and the general public. The act of comparison presumes a standard to which one or the other party must reach, in our case we presume that the media is a *vox populi*, and political parties will be driven towards addressing those voices. However by using political scores such as rile, we further assume the slant, and opinions, of the media to be a gold standard which other parties must concur towards. This is a dangerous notion, both for democracy and free speech. It is a better standard to allow the different parties to differ in their response to an issue, as long as the political parties follow the urgency of a particular issue. Thus by comparing the topic distributions between parties and media, we focus only on the *importance* accorded to each topic by the political parties, allowing them to differentiate the responses according to their political leanings.

## Topic Modelling News Articles

The nearly 14000 news articles were then categorised using unsupervised learning methods. In particular, we used the Latent Dirichlet Allocation to determine the topic probabilities and the term-topic distribution. Formally the model is defined as follows;

Documents are represented as random mixtures over latent topics, where each topic is characterized by a distribution over words. LDA assumes the following generative process for a corpus $D$ consisting of $M$ documents each of length $N_{i}$. The topic distribution for each document $\theta_{i}$ is chosen such that $\theta_{i} \sim Dir(\alpha)$ where $i \in {1, ..., M}$ and $Dir(\alpha)$ is a Dirichlet distribution with the hyper parameter $\alpha$ measuring the *spread* or sparsity of topics. 

$\varphi_{k}$, the word distribution for topic $k$, is then chosen such that $\varphi_{k} \sim Dir(\beta)$  for $k \in {1,..., K}$. Finally for each of the word positions $i,j$, where $j \in {1, \dots ,N_{i}}$, and $i\in {1,\dots ,M}$, a topic $z_{i,j}$ and word $w_{i,j}$ is chosen such that $z_{i,j}\sim Multinomial(\theta _{i})$ and $w_{i,j} \sim Multinomial(\varphi _{z_{i,j}}).$

We use the simple LDA framework, noted above, establish by @Blei2003 without adding a time parameter to allow for dynamic topic modelling. This *muddles the water* a bit, as LDA does not differentiate between the timings of the different topics, and thus may bias the result. Nonetheless, the use of dynamic topics are left for future research. Finally, we set the hyper parameters $\alpha$ as 0.8 and $K$ as 100. 100 topics should cover a breath of the articles, though we are left in the dark regarding the correct distribution. 

Finally, before the text is categorised, all of the articles are cleaned to remove common stop words and punctuation. The words are further *lemmatised* using the Treetagger algorithms derived by @Schmid1994. Lemmatisation of text allows us to control for tenses within the text, as well as reduce the feature space. A brief demonstration of the lemmatisation is given below. 

**Before Lemmatisation;**

```{r lemmatisation, results = "asis"}
temp <- readLines("Data/example.txt") %>%
  stri_split_boundaries()

cat(paste(">", paste(temp[[1]][1:33], collapse = "")))
```

**After Lemmatisation;**

```{r lemmatisation_after, results = "asis"}
cat(paste(">", paste(temp[[2]][1:20], collapse = "")))
```

As seen, the lemmatised text returns all words to their root form, as well as removing digits and punctuation. All of these help in reducing feature space to categorise using LDA.

# Results

## Inter - Party differences

In the graphs below, we can see the change in the above four variables across the time period from 1949 to 2013 for all three political parties for each election year. 

Rile indicates the position of the party in the left-right index, left meaning liberal and right meaning conservative. There are a few clear observations that can be made from the distribution of rile index. First, the two main parties CDU/CSU and SPD are true to their political identity and stay on the right and the left side respectively. However, they both show a tendency to fluctuate between extreme left/right and center every few years. This fluctuation and tendency to meet at the center often showcases the typical phenomenon of game theory. Second, the FDP is often seen to lie at the center, with perfect positioning to appeal the centrist voters and put themselves in the position to be a part of a coalition government.  

```{r, echo=FALSE}
#For rile
plot_rile <- ggplot(df2) +
  geom_line(aes(x = edate, y = rile, colour = partyabbrev))  +
  scale_colour_viridis(discrete = T) +
  theme_minimal() +
  labs(y = "RILE score (rile)") +
  scale_x_date(date_breaks = "10 years", date_labels = "%Y") +
  theme(
    axis.title.x = element_blank()
  )

plot_rile
```

The variable planeco captures three important aspects: Market Regulation, Economic Planning, and Controlled Economy. Higher planeco score means that the government calls for increased consumer protection, increases competition, reduces monopoly, defends small businesses from big companies, takes an active role in economic planning, and introduces price control and minimum wage policies. All three major parties seem to hover around the same range of moderate planeco score. Especially between 1980 and 2000, the score is fairly low due to globalization, development of technology, and opening of trade barriers between countries around the world. However, after 2010, we can see that all parties have adopted a more left-wing approach. We can also see that in recent years, the ideologies of CDU/CSU and that of FDP are more on line with each other.

```{r, echo = FALSE}
#For planeco
plot_planeco <- ggplot(df2) +
  geom_line(aes(x = edate, y = planeco, colour = partyabbrev))  +
  scale_colour_viridis(discrete = T) +
  theme_minimal()+
  labs(y = "Planned Economy (planeco)") +
  scale_x_date(date_breaks = "10 years", date_labels = "%Y") +
  theme(
    axis.title.x = element_blank()
  )


plot_planeco
```
 
The variable markeco represents the policies in favor of free market economy. The fluctuations we see here are common to all three parties. However, CDU/CSU shows that biggest fluctuations and SPD shows the smallest fluctuations. 

```{r, echo = FALSE}
#For markeco
plot_markeco <- ggplot(df2) +
  geom_line(aes(x = edate, y = markeco, colour = partyabbrev)) +
  scale_colour_viridis(discrete = T) +
  theme_minimal()+
  labs(y = "MArket economy (markeco)") +
  scale_x_date(date_breaks = "10 years", date_labels = "%Y") +
  theme(
    axis.title.x = element_blank()
  )


plot_markeco
```

The variable welfare captures equality and welfare state expansion. The three parties vary significantly with each other in this category. 

```{r, echo = FALSE}
#For welfare
plot_welfare <- ggplot(df2) +
  geom_line(aes(x = edate, y = welfare, colour = partyabbrev)) +
  scale_colour_viridis(discrete = T) +
  theme_minimal()+
  labs(y = "Welfare") +
  scale_x_date(date_breaks = "10 years", date_labels = "%Y") +
  theme(
    axis.title.x = element_blank()
  )

plot_welfare
```

## Party and Media

Before we move on to correlate the topic and party distributions, we first look at the breakdowns of the different topics. The 100 topics were labeled, and often spoke of similar topics, though we tried to be as specific as possible with regards to labeling of the different topics. A breakdown of the different topics are given below.

As evident, the topics are unfortunately too broad to compare with political party manifestos. The papers often describe Eurozone policies or security concerns which may be picked up by the different political parties. However, the bulk of the topics tend towards Politics (Wether a party is going through turmoil), Elections (which party can expect how much votes) or Government (Coalitions, fall of coalitions etc.). The topics of elections are particularly interesting, since in may cases they occur months before the actual date of election. 

```{r topic_breakdown}
import("Data/term_breakdown.xlsx") %>%
  dplyr::filter(Topic != "NA") %>%
  group_by(Topic) %>%
  summarise(freq = n()) %>%
  mutate(total = sum(freq),
         freq = freq / total,
         Topic = factor(Topic, levels = Topic[order(-freq)])) %>%
  select(-total) %>%
  ggplot() +
  geom_col(aes(x = Topic, y = freq * 100)) +
  labs(y = "% of Total Topics") +
  scale_fill_viridis(discrete = T) +
  coord_flip() +
  theme_minimal() +
  theme(
    axis.title.y = element_blank()
  )
```

Nearly 30% of our topics talk of general politics, invalidating a bulk of our data. Nonetheless, it would be interesting to view the changes within these topics over time. The figure below plots out the changes in the distribution of these topics over time.

```{r topic_dist, fig.width=7, fig.height=5}
topics <- import("Data/term_breakdown.xlsx") %>%
  dplyr::filter(Topic != "NA") %>%
  select(-term)

import("Data/topic_dist.json") %>%
  group_by(year, text_topics) %>%
  summarise(freq = n()) %>%
  rename(topic = text_topics) %>%
  merge(topics, all.x = T) %>%
  dplyr::filter(!is.na(Topic)) %>%
  ungroup() %>%
  group_by(year) %>%
  mutate(total = sum(freq),
         freq = freq / total * 100) %>%
  ungroup() %>%
  mutate(year = as.factor(year)) %>%
  select(-total) %>%
  ggplot() +
  geom_col(aes(x = year, y = freq, fill = Topic)) +
  scale_fill_viridis(discrete = T) +
  theme_minimal() +
  labs(fill = "Topics") +
  theme(
    axis.title = element_blank(),
    legend.position = "bottom",
    legend.direction = "horizontal"
  )

```

There are a couple of interesting insights that may be gleamed from the graphs. Security is spoken of in a much larger scale close to the 2017 elections than before.This is in stark contrast to the 2005 and 2013 elections when the Eurozone were the dominant topic along with articles related to regional domestic politics. Thus while our topic models works, the end result is too broad to be able to compare with the policies which parties should speak off. 

# Conclusion and Further Work

The major political parties in Germany differ significantly in their approach towards the issue of welfare, market economy and their political positions. Unfortunately due to the limits of our analysis, we could not compare them to the topics of importance brought forward by the media. Nonetheless, there are two key takeaways from our analysis; *firstly* any further research must look at a media source in its entirety and not just a categorisation of these articles. This is unfortunate since it assures significantly greater issues with coding, storing and scraping of these data. 

Finally, the analysis, in some senses, breaks our assumption of media as a *vox populi*; articles in media were entirely focused on the issues of politics and government creation in a stark contrast with the policies undertaken by the government. Future research must therefor tread lightly when looking at the role media plays in informing political positions; while they undoubtedly help, with such focus on regional politics and elections, the question remains; how much? 

# References
