---
title: "Final Manifesto"
author: "Raju Adhikari and Devvart Poddar"
date: "May 13, 2017"
output: pdf_document
---

#Introduction:

In this paper, we aim to understand the intricate relationship between the political parties and news media based on the topics that political parties and media often touch upon. In a more philosophical sense, different political parties are entities with similar goals but different means of getting there. These means can be construed as the mandates of these parties. For example, the mandate of left-wing parties is to achieve social and economic justice through government intervention and welfare systems, while that of right-wing parties is to achieve social and economic justice through less intervention and allowing the market to function freely. While taking up these different approaches (means), the parties often reach out to the voters through a selection of ideas, topics, and verbiage that is unique to their philosophy. In this paper, we analyze these "contents" of political rhetoric of three main German national parties. We will use the Manifesto Dataset to first see the differences between the three parties in terms of different social and political agendas over the years. Second, we will see which topics do these parties use frequently in order to assess their approach in appealing to the voters. Then, we will combine this data with the topic distribution dataset obtained from newspaper articles to analyze the role of media in facilitating the interaction between political parties and voters.


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

setwd("C:/RajuPC/Content Analysis/Final")
  
library(manifestoR)
library(knitr)
library(fBasics)
library(dplyr)
library(ggplot2)

```

```{r, echo = FALSE}
mp_setapikey("manifesto_apikey.txt")

table1 <- mp_coreversions()
kable(table1, align="c", caption="All the Manifesto versions available")

```

```{r, include = FALSE}
df1 <- mp_maindataset(version = "current", south_america = FALSE, download_format = NULL, apikey = NULL)

df2 <- df1 %>%
  dplyr::filter(countryname == "Germany") %>%
  dplyr::filter(partyname == "Social Democratic Party of Germany" | partyname == "Christian Democratic Union/Christian Social Union" | partyname == "Free Democratic Party")
 

unique(df2$partyname)

```

The following table shows the summary of descriptive statistics for the four following variables: rile, planeco, markeco, welfare.

```{r, echo = FALSE}
df3 <- df2 %>%
    select(rile, planeco, markeco, welfare)

table3 <- basicStats(df3)
kable(table3, align="c", caption="Summary of Descriptive Statistics", digits = 2)

```

In the graphs below, we can see the change in the above four variables across the timeperiod from 1949 to 2013 for both political parties for each election year. 

Rile indicates the position of the party in the left-right index, left meaning liberal and right meaning conservative.  

```{r, echo=FALSE}
#For rile
plot_rile <- ggplot(df2) +
  geom_line(aes(x = edate, y = rile, colour = partyname)) 

plot_rile
```

The variable planeco captures three important aspects: Market Regulation, Economing Planning, and Controlled Economy. Higher planeco score means that the government calls for increased consumer protection, increases competition, reduces monopoly, defends small businesses from big companies, takes an active role in economic planning, and introduces price control and minimum wage policies.

```{r, echo = FALSE}
#For planeco
plot_planeco <- ggplot(df2) +
  geom_line(aes(x = edate, y = planeco, colour = partyname)) 

plot_planeco
```
 
The variable markeco represents the policies in favor of free market economy.

```{r, echo = FALSE}
#For markeco
plot_markeco <- ggplot(df2) +
  geom_line(aes(x = edate, y = markeco, colour = partyname)) 

plot_markeco
```

The variable welfare captures equality and welfare state expansion.

```{r, echo = FALSE}
#For welfare
plot_welfare <- ggplot(df2) +
  geom_line(aes(x = edate, y = welfare, colour = partyname)) +
  scale_x_date(date_breaks = "8 years")
plot_welfare
```


#Part IV: Alternate left-right measures:
One alternative way for rile as proposed by Lowe et al. 2010 suggests taking the log of the ratio of Right and Left. For this we combine as all the variables that make up Right and Left separately using the Codebook, then take a ratio of right to left and perform a log on it.

Right (R) = per104 + per201 + per203 + per305 + per401 + per402 + per407 + per414 + per505 + per601 + per603 + per605 + per606

Left (L) = per103 + per105 + per106 + per107 + per403 + per404 + per406 + per412 + per413 + per504 + per506 + per701 + per202

Alternative Rile (alt) = log (R/L)

The graph below does not show any significant change in comparison to normal rile calculated above in section II.
```{r, echo=FALSE}
alternate <- df2 %>%
  mutate(R = per104 + per201 + per203 + per305 + per401 + per402 + per407 + per414 + 
           per505 + per601 + per603 + per605 + per606) %>%
  mutate (L = per103 + per105 + per106 + per107 + per403 + per404 + per406 + 
                   per412 + per413 + per504 + per506 + per701 + per202) %>%
  mutate(alt = log(R / L))
```

```{r, echo = FALSE}

plot_altrile <- ggplot(alternate) +
  geom_line(aes(x = edate, y = alt, colour = partyname)) 

plot_altrile

```

#Part V: Most Unreliable categories:
Mikhaylov et al. 2011 underscore the presence of several unreliable categories. For the left side of the rile scale they point out 202 and 701 as extremely unreliable and for the right side they point out 605 and 305 as extremely unreliable due to their extremley low kappa coefficient. After the removal of the unreliable categories, the rile graph below shows some significant changes.


```{r, echo=FALSE}
correction <- df2 %>%
  mutate(R = per104 + per201 + per203 + per401 + per402 + per407 + per414 + 
           per505 + per601 + per603 + per606) %>%
  mutate (L = per103 + per105 + per106 + per107 + per403 + per404 + per406 + 
                   per412 + per413 + per504 + per506) %>%
  mutate(correct = log(R / L))
```

```{r, echo = FALSE}

plot_correctrile <- ggplot(correction) +
  geom_line(aes(x = edate, y = correct, colour = partyname)) 

plot_correctrile

```




